Type Refinements for the Working Class

### 2015-11-15 paper.tex
Restore (changed version) of lcs definition

Then, a \emph{lazy computation system} (lcs) is a lazy computation language
$\Match{L}{\Pair{\Sigma}{\CanOperators}}$ along with an $\SCtx$-indexed
$\equiv_\alpha$-functional evaluation relation
$\EvalN{\Upsilon}{\tau}{n}{M}{N}$ presupposing $\Member{n}{\Naturals}$,
$\Member{M}{\Exprs_\tau(\Upsilon)}$ and $\Member{N}{\Values_\tau(\Upsilon)}$,
expressing that $M$ evaluates to $N$ in $n$ steps.

%% \begin{remark}
%%
%%   Formally, the evaluation relation is given in our logical framework by a
%%   presheaf of evaluation rules $\Of{\mathfrak{R}^\tau_\Downarrow}{\mathbb{J}}$,
%%   such that the judgment
%%   $\HypJ{\Pow{\mathfrak{R}^\tau_\Downarrow}}{\Exprs_\tau, \Values_\tau,
%%   \NaturalsPsh}$ is globally evident where $\NaturalsPsh$ is the constant
%%   presheaf $\MapsTo{\Upsilon}{\Naturals}$. In other words, we have a family of
%%   internal judgments $\Of{[\Downarrow_\tau](\Upsilon)}{\int_{\Upsilon'}
%%   \Upsilon\inj\Upsilon'\Rightarrow\Pow{\mathfrak{R}^\tau_\Downarrow}}$
%%
%%
%% shall be evident by means of some internal
%% family of judgments $[\Downarrow_\tau]$, where $\NaturalsPsh$ is the constant
%% presheaf $\MapsTo{\Upsilon}{\Naturals}$. In other words, we shall forevermore know
%% what it means to know that some expression evaluates to some value in $n$
%% steps.
%% \end{remark}
%%
%% We will write $\Eval{\Upsilon}{\tau}{M}{N}$ to mean that there exists an $n$
%% such that $\EvalN{\Upsilon}{\tau}{n}{M}{N}$; in other words, the judgment is
%% interpreted as the following presheaf:
%% \[
%%   \Define{
%%     \left(\Upsilon\parallel M\Downarrow_\tau N\right)(w)
%%   }{
%%     \int^n[\Downarrow_\tau](w,M,N,n)
%%   }
%% \]
%%
%%
%% By this token, the derivations of $\EvalN{\Upsilon}{\tau}{n}{M}{N}$ at
%% $w$ are the set $[\Downarrow_\tau](w,M,N,n)$; we write
%% $\Eval{\Upsilon}{\tau}{M}{N}$ for the judgment
%% $\int^n[\Downarrow_\tau](-,M,N,n)$
%

>>>>

Then, a \emph{lazy computation system} (lcs) is a lazy computation language
$\Match{L}{\Pair{\Sigma}{\CanOperators}}$ along with an $\SCtx$-indexed
$\equiv_\alpha$-functional evaluation relation
$\EvalN{\Upsilon}{\tau}{n}{M}{N}$ presupposing $\Member{n}{\Naturals}$,
$\Member{M}{\Exprs_\tau(\Upsilon)}$ and $\Member{N}{\Values_\tau(\Upsilon)}$,
expressing that $M$ evaluates to $N$ in $n$ steps.  We will write
$\Eval{\Upsilon}{\tau}{M}{N}$ to mean that there exists an $n$ such that
$\EvalN{\Upsilon}{\tau}{n}{M}{N}$.

 \begin{remark}
   Formally, the evaluation relation is given in our logical framework by a
   global internal judgment $\Of{\Downarrow_\tau}{\int_\SCtx
   \Omega^{\Exprs_\tau\times\Values_\tau\times\NaturalsPsh}}$, where
   $\NaturalsPsh$ is the constant presheaf $\MapsTo{\Upsilon}{\Naturals}$.
   Then, we know $\EvalN{\Upsilon}{\tau}{n}{M}{N}$ just when the
   externalization $\Embed{\Downarrow_\tau}(M,N,n)$ is evident at $\Upsilon$.
 \end{remark}
